Refinements for open automata

### 2022-12-20 2021-Refinement/paper/refinementarticleV2.tex
refine
current version

Which can be rewritten as:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
\end{multline*}

@@

\item Lastly, we have to prove the satisfaction of the deadlock reduction condition:
According to the relation between A2 and A3 we have for all

%\begin{multline*}
%\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( %\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} %\fguard{t_2}  )
%\end{multline*}

@@

\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}

>>>>

Which can be rewritten as:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
\end{multline*}

@@

\item Lastly, we have to prove the satisfaction of the deadlock reduction condition. According to the relation between A2 and A3 we have for all $\mpar{s_{2p},s_3} \in S_2\times S_3$
\begin{multline*}
 V_2 \uplus V_3  \vdash R\mpar{s_{2p},s_3} \implies ( \bigvee_\subbox{t_1 \in \fOT{s_{2p}}} \fguard{t_{2p}} ) \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
\end{multline*}

\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
\end{multline*}

\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( %\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} %\fguard{t_2}  )
\end{multline*}

@@

%\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
